An empirical study of fixation for strategies in the Iterated Prisoner's Dilemma

### 2017-10-24 tex/list_of_players.tex
Update grudger memory depth
Add state number to appendix for FSM players
Note that this is not necessarily the smallest number of states. That in
itself is a harder problem.

\item Evolved FSM 16 - \textit{Deterministic} - \textit{Memory depth}: 16. \cite{axelrodproject}
\item Evolved FSM 16 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: 16. \cite{axelrodproject}
\item Evolved FSM 4 - \textit{Deterministic} - \textit{Memory depth}: 4. \cite{axelrodproject}

@@

\item FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 0, C(\textbf{TF3}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\).
\item FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 0, C(\textbf{TF2}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\).
\item FSM Player: [(0, 'C', 7, 'C'), (0, 'D', 1, 'C'), (1, 'C', 11, 'D'), (1, 'D', 11, 'D'), (2, 'C', 8, 'D'), (2, 'D', 8, 'C'), (3, 'C', 3, 'C'), (3, 'D', 12, 'D'), (4, 'C', 6, 'C'), (4, 'D', 3, 'C'), (5, 'C', 11, 'C'), (5, 'D', 8, 'D'), (6, 'C', 13, 'D'), (6, 'D', 14, 'C'), (7, 'C', 4, 'D'), (7, 'D', 2, 'D'), (8, 'C', 14, 'D'), (8, 'D', 8, 'D'), (9, 'C', 0, 'C'), (9, 'D', 10, 'D'), (10, 'C', 8, 'C'), (10, 'D', 15, 'C'), (11, 'C', 6, 'D'), (11, 'D', 5, 'D'), (12, 'C', 6, 'D'), (12, 'D', 9, 'D'), (13, 'C', 9, 'D'), (13, 'D', 8, 'D'), (14, 'C', 8, 'D'), (14, 'D', 13, 'D'), (15, 'C', 4, 'C'), (15, 'D', 5, 'C')], 0, C(\textbf{TF1}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\).

@@

\item Fortress3 - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2006b}
\item Fortress4 - \textit{Deterministic} - \textit{Memory depth}: 4. \cite{Ashlock2006b}

@@

\item Grudger - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980, Banks1990, Beaufils1997, Berg2015, Li2011}

@@

\item Predator - \textit{Deterministic} - \textit{Memory depth}: 9. \cite{Ashlock2006b}

@@

\item Pun1 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Ashlock2006}

@@

\item Raider - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2014}

@@

\item Ripoff - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Ashlock2008}

@@

\item SolutionB1 - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2015}
\item SolutionB5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{Ashlock2015}

@@

\item Thumper - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Ashlock2008}

>>>>

\item Evolved FSM 16 - \textit{Deterministic} - \textit{Memory depth}: 16 - \textit{Number of states}: 14. \cite{axelrodproject}
\item Evolved FSM 16 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: 16 - \textit{Number of states}: 14. \cite{axelrodproject}
\item Evolved FSM 4 - \textit{Deterministic} - \textit{Memory depth}: 4 - \textit{Number of states}: 4. \cite{axelrodproject}

@@

\item FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 0, C(\textbf{TF3}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 8.
\item FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 0, C(\textbf{TF2}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 16.
\item FSM Player: [(0, 'C', 7, 'C'), (0, 'D', 1, 'C'), (1, 'C', 11, 'D'), (1, 'D', 11, 'D'), (2, 'C', 8, 'D'), (2, 'D', 8, 'C'), (3, 'C', 3, 'C'), (3, 'D', 12, 'D'), (4, 'C', 6, 'C'), (4, 'D', 3, 'C'), (5, 'C', 11, 'C'), (5, 'D', 8, 'D'), (6, 'C', 13, 'D'), (6, 'D', 14, 'C'), (7, 'C', 4, 'D'), (7, 'D', 2, 'D'), (8, 'C', 14, 'D'), (8, 'D', 8, 'D'), (9, 'C', 0, 'C'), (9, 'D', 10, 'D'), (10, 'C', 8, 'C'), (10, 'D', 15, 'C'), (11, 'C', 6, 'D'), (11, 'D', 5, 'D'), (12, 'C', 6, 'D'), (12, 'D', 9, 'D'), (13, 'C', 9, 'D'), (13, 'D', 8, 'D'), (14, 'C', 8, 'D'), (14, 'D', 13, 'D'), (15, 'C', 4, 'C'), (15, 'D', 5, 'C')], 0, C(\textbf{TF1}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 16.

@@

\item Fortress3 - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 3. \cite{Ashlock2006b}
\item Fortress4 - \textit{Deterministic} - \textit{Memory depth}: 4 - \textit{Number of states}: 4. \cite{Ashlock2006b}

@@

\item Grudger - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980, Banks1990, Beaufils1997, Berg2015, Li2011}

@@

\item Predator - \textit{Deterministic} - \textit{Memory depth}: 9 - \textit{Number of states}: 9. \cite{Ashlock2006b}

@@

\item Pun1 - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 2. \cite{Ashlock2006}

@@

\item Raider - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 4. \cite{Ashlock2014}

@@

\item Ripoff - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 3. \cite{Ashlock2008}

@@

\item SolutionB1 - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 3. \cite{Ashlock2015}
\item SolutionB5 - \textit{Deterministic} - \textit{Memory depth}: 5 - \textit{Number of states}: 6. \cite{Ashlock2015}

@@

\item Thumper - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 2. \cite{Ashlock2008}
